Minimizing post shock forecasting error using disparate information

### 2020-06-07 manuscript/manuscript.tex
additional explanation to data analysis results with COVID-19

>>>>

However, from another perspective, this phenomenon can be explained by the fact that the donor pool is not constructed to be similar enough to the time series of interest. The shock on 2020-03-09 occurred with the pandemic caused by  COVID-19. It is difficult to find available stock market time series data that were generated under a similar setting.
